---
title: "Figures and tables for Idaho antibiotic use project"
author: "Jeremy Boyd"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Distribution of claims per 1K beneficiary

- Second and fourth figures are claims_1k where missing beneficiary counts have been imputed.
- Last two figures show that normality improves when claims_1k is logged.

```{r, echo = FALSE, error = FALSE, message = FALSE, warning = FALSE}

# TODO: better way to do this is to come up with a pd dataset that's 1 row per prescriber per drug class per year. That dataset has lots of columns, including Tot_Benes, Tot_Benes_Imp, claims_1k, claims_1k imp. Then have a general summary function that takes this dataset and a group_by specification. It will output summaries for lots of different values that are both weighted and unweighted. If weighted, should be versions using Tot_Benes (which means all rows with fewer than 11 will be omitted), and Tot_Benes_Imp (which means that we get to keep those rows). For each different type of summary we want a col that describes the summary type--e.g., no imputation, weighted; yes imputation, unweighted, etc.


#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
#### Compute claims / 1K beneficiaries ####
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

# Tot_Clms: The number of Medicare Part D claims. This includes original
# prescriptions and refills. Get this from by-provider-and-drug.
# Tot_Benes: The total number of unique Medicare Part D beneficiaries with at
# least one claim for the drug. Get this from by-provider. Definition "the drug"
# is a bit misleading, since in the by-provider dataset we're getting a count of
# beneficiaries who had a prescription for *any* drug.

# Read in generic drug bank
generics <- read_feather("Generic drug bank.feather")

# Read in 2019 provider types
p_types <- read_feather("Idaho 2019 provider type bank.feather")

# Read in by-provider-and-drug dataset. This has claims numbers for computing
# claims per 1K beneficiaries.
pd <- read_feather("Idaho prescribers by provider & drug data.feather") %>%
    
    # Join in coding for drug classes from generics
    left_join(generics, by = "Gnrc_Name") %>%
    select(Prscrbr_NPI, year, Gnrc_Name, Tot_Clms, Antibiotic:Other)
    
# Read in by-provider dataset. This has beneficiary numbers for computing claims
# per 1K beneficiaries. Join in prescriber type (only have this for 2019 so
# far).
p_benes <- read_feather("Idaho prescribers by provider data.feather") %>%
    select(Prscrbr_NPI, year, Tot_Benes, Prscrbr_RUCA, Prscrbr_Type,
           Bene_Avg_Age, Bene_Feml_Cnt, Bene_Avg_Risk_Scre) %>%
    mutate(Tot_Benes_Imp = Tot_Benes) %>%
    left_join(p_types, by = c("Prscrbr_Type", "year"))

# Separate into tables based on whether Tot_Benes is defined or not
yes_benes <- p_benes %>% filter(!is.na(Tot_Benes))
no_benes <- p_benes %>% filter(is.na(Tot_Benes))

# For NA values, impute
# NOTE: Can we also impute values for other cols? Most of these are subject to
# the > 10 beneficiary rule.
set.seed(1)
no_benes$Tot_Benes_Imp <- round(rnorm(n = nrow(no_benes), mean = 5.5, sd = 1.5))
no_benes <- no_benes %>%
    mutate(Tot_Benes_Imp = case_when(
        Tot_Benes_Imp > 10 ~ 10,
        Tot_Benes_Imp < 1 ~ 1,
        TRUE ~ Tot_Benes_Imp))

# Recombine to form p_benes with imputed values for NA Tot_Benes
p_benes <- bind_rows(yes_benes, no_benes) %>%
    mutate(percent_fem = Bene_Feml_Cnt / Tot_Benes_Imp * 100)

# Drug classes that we want to compute claims per 1K beneficiaries for
drug_classes <- names(generics)[2:length(names(generics))]

# Summarize across drugs to get total claims per drug *class*. Join in
# beneficiary data.
pd_claims_1k <- map_dfr(drug_classes, function(class) {
    message(paste0("Getting claim & beneficiary data for class ", class, "..."))
    claims_year(data = pd, drug_class = class) %>%
        left_join(p_benes, by = c("Prscrbr_NPI", "year")) %>%
        mutate(claims_1k = tot_clms / (Tot_Benes_Imp / 1000),
               log_claims_1k = log(claims_1k),
               claims_1k_imp = tot_clms / (Tot_Benes_Imp / 1000),
               log_claims_1k_imp = log(claims_1k_imp),
               class = class)
}) 

#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
#### Model claims / 1K beneficiaries ####
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

# Use logged, imputed versions of claims 1k. Logged versions of claims_1k are
# more normal. Versions of claims_1k with and without imputation for NAs have
# nearly identical distributions.
pd_claims_1k %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = claims_1k)) +
    geom_density()
pd_claims_1k %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = claims_1k_imp)) +
    geom_density()
pd_claims_1k %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = log_claims_1k)) +
    geom_density()
pd_claims_1k %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = log_claims_1k_imp)) +
    geom_density()

# Model log_claims_1k_imp ~ year for all classes..
# NOTE that I'm using weights in all models to take into account that some
# providers have more beneficiaries.
year_effects <- map_dfr(drug_classes, function(class) {
    class_data <- pd_claims_1k %>%
        filter(class == !!class)
    lm(log_claims_1k_imp ~ year,
       data = class_data,
       weights = Tot_Benes_Imp) %>%
    tidy() %>%
    mutate(class = class)
}) %>%
    mutate(
        `p < 0.05` = if_else(p.value < 0.05, "*", "")) %>%
    filter(term == "year") %>%
    arrange(p.value)

# Summarize across providers
pd_claims_1k_sum <- map_dfr(drug_classes, function(class) {
    message(paste0("Summarizing class ", class, "..."))
    class_data <- pd_claims_1k %>%
        filter(class == !!class)
    claims_1k_summary(data = class_data, outcome_var = "claims_1k_imp") %>%
        mutate(class = !!class)
})

# Compute percent decrease from 2013 to 2019
change <- pd_claims_1k_sum %>%
    filter(year %in% c(min(pd_claims_1k_sum$year),
                       max(pd_claims_1k_sum$year))) %>%
    select(year, mean, class) %>%
    pivot_wider(names_from = "year", values_from = "mean") %>%
    mutate(percent_decrease = (`2013` - `2019`) / `2013` * 100)

```

### Changes in claims per 1K beneficiaries over time

- Beneficiary counts are NA for all counts < 11. This potentially biases the analysis by ignoring small providers.
- To deal with potential bias, missing beneficiary counts were imputed as normal(mean = 5.5, sd = 1.5), with min = 1 and max = 10.
- Computation of means and linear models use beneficiary counts as weights.
- Models are of log(claims_1k).

```{r, echo = FALSE, error = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 11}

# Plot claims_1k ~ year, with annotations showing percent decrease and p-values
# for statsig decreases.
# NOTE: Using claims_1k_imp seems to lead to a couple more statsig results,
# including an *increase* in the use of tetracycline.
pd_claims_1k_sum %>%
    left_join(year_effects, by = "class") %>%
    left_join(change %>% select(class, percent_decrease), by = "class") %>%
    mutate(class2 = case_when(
        `p < 0.05` == "*" & percent_decrease > 0 ~ paste0(
            class, "\n",
            round(percent_decrease), "% decrease\n",
            "p = ", format(p.value, scientific = TRUE, digits = 3)),
        `p < 0.05` == "*" & percent_decrease < 0 ~  paste0(
            class, "\n",
            round(percent_decrease * -1), "% increase\n",
            "p = ", format(p.value, scientific = TRUE, digits = 3)),
        TRUE ~ class),
        class2 = fct_relevel(class2,
                             "Other",
                             after = Inf)) %>%
    ggplot(mapping = aes(x = year,
                         y = mean,
                         group = class2,
                         color = class2)) +
    geom_errorbar(aes(ymin = mean - se,
                      ymax = mean + se),
                  width = 0.2, size = 0.4, color = "gray50") +
    geom_line() +
    scale_x_continuous(breaks = seq(min(pd_claims_1k_sum$year),
                                    max(pd_claims_1k_sum$year), 2)) +
    scale_y_continuous(breaks = seq(0, 1000, 100),
                       limits = c(0, 400)) +
    facet_wrap(~ class2, ncol = 4, scales = "free") +
    labs(x = "Year",
         y = "Claims\nper 1K\nbeneficiaries",
         color = "Class") +
    theme(legend.position = "none")

```

### Weighted versus unweighted statistics

- All figures are for class = Antibiotic.
- Missing beneficiary counts are imputed.
- Using unweighted seems to underestimate beneficiary age and HCC score, while overestimating mean claims per 1K beneficiaries.

```{r, echo = FALSE, error = FALSE, message = FALSE, warning = FALSE}
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
#### Tables ####
#++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

# Use pd_claims_1k, which has claims from by-provider-and-drug, and beneficiary
# counts from by-provider.
year_class_wt <- summarize_provider_data(
    providers_data = pd_claims_1k,
    type = "weighted")
year_class_unwt <- summarize_provider_data(
    providers_data = pd_claims_1k,
    type = "unweighted")
    
# Compare weighted and unweighted
# Number of providers, antibiotics
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = n_providers, color = type,
           group = type)) +
    geom_line()

# Mean beneficiary count, antibiotics. These are identical, so lines are
# overplotted. How does beneficiary count get higher in this version versus the one from May 2? Here I'm replacing NA Tot_Benes with values from 1-10, which are all small numbers. Seems like this should make the mean beneficiary count go down rather than up. Before I was using Tot_Benes from the by-provider table. This time I'm using it after joining to by-provider-and-drug. If I'm doing this correctly the beneficiary statistics should stat the same no matter what the drug class is because it's always the same info coming from the by-providers table. Check this...
# Crap! changes with drug. What's going on...?
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_ben_cnt, color = type,
                         group = type)) +
    geom_line() +
    geom_errorbar(aes(ymin = mean_ben_cnt - sd_ben_cnt,
                      ymax = mean_ben_cnt + sd_ben_cnt),
                  width = 0.2,
                  size = 0.5)

# Beneficiary age, anbibiotics
pd <- position_dodge(0.25)
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_ben_age, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_ben_age - sd_ben_age,
                      ymax = mean_ben_age + sd_ben_age),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Percent female, antibiotics
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_percent_fem, color = type,
                         group = type)) +
    geom_line()

# Mean HCC, anbibiotics
pd <- position_dodge(0.25)
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_hcc, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_hcc - sd_hcc,
                      ymax = mean_hcc + sd_hcc),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Mean number of claims, antibiotics
pd <- position_dodge(0.25)
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_clms, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_clms - sd_clms,
                      ymax = mean_clms + sd_clms),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Mean claims per 1K beneficiaries, anbitiotics
pd <- position_dodge(0.25)
bind_rows(year_class_wt, year_class_unwt) %>%
    filter(class == "Antibiotic") %>%
    ggplot(mapping = aes(x = year, y = mean_clms_1k, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_clms_1k - sd_clms_1k,
                      ymax = mean_clms_1k + sd_clms_1k),
                  position = pd,
                  width = 0.2,
                  size = 0.2)
```

<br>
<br>

### Weighted beneficiary statistics by year

- All stats computed with missing beneficiary counts imputed.

```{r tables, echo = FALSE, error = FALSE, message = FALSE}

# Example slide 11 table
# Turn this into a function to make this table. First col in table is the "by" variable--could be years, provider types, provider gender, etc.
year_class_wt %>%
    filter(class == "Antibiotic") %>%
    arrange(desc(year)) %>%
    mutate(
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        ben_cnt_range = paste0(
            format(min_ben_cnt, nsmall = 0, digits = 2, big.mark = ","),
            "-",
            format(max_ben_cnt, nsmall = 0, digits = 2, big.mark = ",")),
        mean_ben_age = paste0(
            format(mean_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_percent_fem = format(mean_percent_fem, nsmall = 1, digits = 2),
        mean_hcc = paste0(
            format(mean_hcc, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_hcc, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        hcc_range = paste0(
            format(min_hcc, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_hcc, nsmall = 2, digits = 2, big.mark = ","))) %>%
    select(year, mean_ben_cnt, ben_cnt_range, mean_ben_age, mean_percent_fem, mean_hcc,
           hcc_range) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Year", "Mean (SD) Beneficiary Count", "Range Beneficiary Count", "Mean (SD) Beneficiary Age", "Sex (% Female)", "Mean (SD) Beneficiary HCC Score", "Range Beneficiary HCC Score"))

```

<br>
<br>

### Weighted antibiotic use statistics by year

- All stats computed with missing beneficiary counts imputed.

```{r, echo = FALSE, error = FALSE, message = FALSE}
# Example slide 12
year_class_wt %>%
    filter(class == "Antibiotic") %>%
    arrange(desc(year)) %>%
    mutate(
        mean_clms = paste0(
            format(mean_clms, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_clms, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_clms_1k = paste0(
            format(mean_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        range_clms_1k = paste0(
            format(min_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_clms_1k, nsmall = 2, digits = 2, big.mark = ","))
    ) %>%
    select(year, mean_clms, mean_ben_cnt, mean_clms_1k, range_clms_1k) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Year", "Mean (SD) Antibiotic Claims", "Mean (SD) Beneficiary Count", "Mean Antibiotic Claims / 1K Beneficiaries", "Range Antibiotic Claims / 1K Beneficiaries"))

```

<br>
<br>

### Weighted 2019 beneficiary statistics by prescriber type

- All stats computed with missing beneficiary counts imputed.

```{r, echo = FALSE, error = FALSE, message = FALSE}

# Table describing beneficiaries by prescriber type
summarize_provider_data(
    providers_data = pd_claims_1k,
    grouping_var = "Std_Provider_Type",
    type = "weighted") %>%
    filter(class == "Antibiotic", year == 2019) %>%
    arrange(desc(mean_ben_cnt)) %>%
    mutate(
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        ben_cnt_range = paste0(
            format(min_ben_cnt, nsmall = 0, digits = 2, big.mark = ","),
            "-",
            format(max_ben_cnt, nsmall = 0, digits = 2, big.mark = ",")),
        mean_ben_age = paste0(
            format(mean_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_percent_fem = format(mean_percent_fem, nsmall = 1, digits = 2),
        mean_hcc = paste0(
            format(mean_hcc, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_hcc, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        hcc_range = paste0(
            format(min_hcc, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_hcc, nsmall = 2, digits = 2, big.mark = ","))) %>%
    select(Std_Provider_Type, mean_ben_cnt, ben_cnt_range, mean_ben_age, mean_percent_fem, mean_hcc,
           hcc_range) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Prescriber Type", "Mean (SD) Beneficiary Count", "Range Beneficiary Count", "Mean (SD) Beneficiary Age", "Sex (% Female)", "Mean (SD) Beneficiary HCC Score", "Range Beneficiary HCC Score"))

```

<br>
<br>

### Weighted 2019 antibiotic use statistics by prescriber type

- All stats computed with missing beneficiary counts imputed.

```{r, echo = FALSE, error = FALSE, message = FALSE}

# Table describing antibiotic prescribing by provider type
summarize_provider_data(
    providers_data = pd_claims_1k,
    grouping_var = "Std_Provider_Type",
    type = "weighted") %>%
    filter(class == "Antibiotic", year == 2019) %>%
    arrange(desc(mean_clms_1k)) %>%
    mutate(
        mean_clms = paste0(
            format(mean_clms, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_clms, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_clms_1k = paste0(
            format(mean_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        range_clms_1k = paste0(
            format(min_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_clms_1k, nsmall = 2, digits = 2, big.mark = ","))
    ) %>%
    select(Std_Provider_Type, mean_clms, mean_ben_cnt, mean_clms_1k, range_clms_1k) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Prescriber Type", "Mean (SD) Antibiotic Claims", "Mean (SD) Beneficiary Count", "Mean Antibiotic Claims / 1K Beneficiaries", "Range Antibiotic Claims / 1K Beneficiaries"))

```
