---
title: "Figures and tables for Idaho antibiotic use project"
author: "Jeremy Boyd"
date: "5/2/2022"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r figures, echo = FALSE, error = FALSE, message = FALSE}


# UPDATE TO USE NUMERATORS FROM PD DATA


# Read in by-providers data
p <- read_feather("Idaho prescribers by provider data.feather")

# Compute weighted & unweighted summary tables by year
year_wt <- summarize_provider_data(providers_data = p,
                                   type = "weighted")
year_unwt <- summarize_provider_data(providers_data = p,
                                   type = "unweighted")

# Compare weighted and unweighted
# Number of providers
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = n_providers, color = type,
           group = type)) +
    geom_line()

# Mean beneficiary count. These are identical, so lines are overplotted.
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_ben_cnt, color = type,
                         group = type)) +
    geom_line() +
    geom_errorbar(aes(ymin = mean_ben_cnt - sd_ben_cnt,
                      ymax = mean_ben_cnt + sd_ben_cnt),
                  width = 0.2,
                  size = 0.5)

# Beneficiary age
pd <- position_dodge(0.25)
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_ben_age, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_ben_age - sd_ben_age,
                      ymax = mean_ben_age + sd_ben_age),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Percent female
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_percent_fem, color = type,
                         group = type)) +
    geom_line(position = pd)

# Mean HCC
pd <- position_dodge(0.25)
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_hcc, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_hcc - sd_hcc,
                      ymax = mean_hcc + sd_hcc),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Mean number of antibiotic claims
pd <- position_dodge(0.25)
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_ant_clms, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_ant_clms - sd_ant_clms,
                      ymax = mean_ant_clms + sd_ant_clms),
                  position = pd,
                  width = 0.2,
                  size = 0.2)

# Mean antibiotic claims per 1K beneficiaries
pd <- position_dodge(0.25)
bind_rows(year_wt, year_unwt) %>%
    ggplot(mapping = aes(x = year, y = mean_ant_clms_1k, color = type,
                         group = type)) +
    geom_line(position = pd) +
    geom_errorbar(aes(ymin = mean_ant_clms_1k - sd_ant_clms_1k,
                      ymax = mean_ant_clms_1k + sd_ant_clms_1k),
                  position = pd,
                  width = 0.2,
                  size = 0.2)
```

<br>
<br>

### Weighted beneficiary statistics by year

```{r tables, echo = FALSE, error = FALSE, message = FALSE}

# Example slide 11 table
# Turn this into a function to make this table. First col in table is the "by" variable--could be years, provider types, provider gender, etc.
year_wt %>%
    arrange(desc(year)) %>%
    mutate(
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        ben_cnt_range = paste0(
            format(min_ben_cnt, nsmall = 0, digits = 2, big.mark = ","),
            "-",
            format(max_ben_cnt, nsmall = 0, digits = 2, big.mark = ",")),
        mean_ben_age = paste0(
            format(mean_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_percent_fem = format(mean_percent_fem, nsmall = 1, digits = 2),
        mean_hcc = paste0(
            format(mean_hcc, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_hcc, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        hcc_range = paste0(
            format(min_hcc, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_hcc, nsmall = 2, digits = 2, big.mark = ","))) %>%
    select(year, mean_ben_cnt, ben_cnt_range, mean_ben_age, mean_percent_fem, mean_hcc,
           hcc_range) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Year", "Mean (SD) Beneficiary Count", "Range Beneficiary Count", "Mean (SD) Beneficiary Age", "Sex (% Female)", "Mean (SD) Beneficiary HCC Score", "Range Beneficiary HCC Score"))

```

<br>
<br>

### Weighted antibiotic use statistics by year

Note: In this table and all of the tables below, claims quantities are coming from the by-provider data. For consistency, should recompute using claims from by-provider-and-drug.

```{r, echo = FALSE, error = FALSE, message = FALSE}
# Example slide 12
year_wt %>%
    arrange(desc(year)) %>%
    mutate(
        mean_ant_clms = paste0(
            format(mean_ant_clms, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ant_clms, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ant_clms_1k = paste0(
            format(mean_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        range_ant_clms_1k = paste0(
            format(min_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","))
    ) %>%
    select(year, mean_ant_clms, mean_ben_cnt, mean_ant_clms_1k, range_ant_clms_1k) %>%
    datatable(
        options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Year", "Mean (SD) Antibiotic Claims", "Mean (SD) Beneficiary Count", "Mean Antibiotic Claims / 1K Beneficiaries", "Range Antibiotic Claims / 1K Beneficiaries"))

```

<br>
<br>

### Weighted 2019 beneficiary statistics by prescriber type

```{r, echo = FALSE, error = FALSE, message = FALSE}

# Bank of prescriber types
types <- read_feather("Idaho 2019 provider type bank.feather")

# Compute weighted values by Karl's Standard_Provider_Type
prscrbr_type_2019 <- summarize_provider_data(
    providers_data = p %>%
        filter(year == 2019) %>%
        left_join(types, by = "Prscrbr_Type"),
    grouping_var = "Standard_Provider_Type",
    type = "weighted") %>%
    mutate(Prscrbr_Type = Standard_Provider_Type) %>%
    arrange(desc(n_providers))

# Table describing beneficiaries by prescriber type
prscrbr_type_2019 %>% 
    arrange(desc(mean_ben_cnt)) %>%
    mutate(
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        ben_cnt_range = paste0(
            format(min_ben_cnt, nsmall = 0, digits = 2, big.mark = ","),
            "-",
            format(max_ben_cnt, nsmall = 0, digits = 2, big.mark = ",")),
        mean_ben_age = paste0(
            format(mean_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_age, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_percent_fem = format(mean_percent_fem, nsmall = 1, digits = 2),
        mean_hcc = paste0(
            format(mean_hcc, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_hcc, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        hcc_range = paste0(
            format(min_hcc, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_hcc, nsmall = 2, digits = 2, big.mark = ","))) %>%
    select(Prscrbr_Type, mean_ben_cnt, ben_cnt_range, mean_ben_age, mean_percent_fem, mean_hcc,
           hcc_range) %>%
    datatable(
        # options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Prescriber Type", "Mean (SD) Beneficiary Count", "Range Beneficiary Count", "Mean (SD) Beneficiary Age", "Sex (% Female)", "Mean (SD) Beneficiary HCC Score", "Range Beneficiary HCC Score"))

```

<br>
<br>

### Weighted 2019 antibiotic use statistics by prescriber type

```{r, echo = FALSE, error = FALSE, message = FALSE}

# Table describing antibiotic prescribing by provider type
prscrbr_type_2019 %>% 
    arrange(desc(mean_ant_clms_1k)) %>%
    mutate(
        mean_ant_clms = paste0(
            format(mean_ant_clms, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ant_clms, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ben_cnt = paste0(
            format(mean_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ben_cnt, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        mean_ant_clms_1k = paste0(
            format(mean_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            " (",
            format(sd_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            ")"),
        range_ant_clms_1k = paste0(
            format(min_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
            "-",
            format(max_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","))
    ) %>%
    select(Prscrbr_Type, mean_ant_clms, mean_ben_cnt, mean_ant_clms_1k, range_ant_clms_1k) %>%
    datatable(
        # options = list(dom = "t"),
        rownames = FALSE,
              colnames = c("Prescriber Type", "Mean (SD) Antibiotic Claims", "Mean (SD) Beneficiary Count", "Mean Antibiotic Claims / 1K Beneficiaries", "Range Antibiotic Claims / 1K Beneficiaries"))

```




```{r, echo = FALSE, error = FALSE, message = FALSE}

# <br>
# <br>

### Same table as above, produced by kable()

# prscrbr_type_2019 %>%
#     arrange(desc(mean_ant_clms_1k)) %>%
#     mutate(
#         range_ant_clms_1k = paste0(
#             format(min_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","),
#             "-",
#             format(max_ant_clms_1k, nsmall = 2, digits = 2, big.mark = ","))
#     ) %>%
#     select(Prscrbr_Type, mean_ant_clms, mean_ben_cnt, mean_ant_clms_1k, range_ant_clms_1k) %>%
#     kable(digits = 2,
#           row.names = FALSE,
#           col.names = c("Prescriber Type", "Mean (SD) Antibiotic Claims", "Mean (SD) Beneficiary Count", "Mean Antibiotic Claims / 1K Beneficiaries", "Range Antibiotic Claims / 1K Beneficiaries"),
#           align = "l")

```

